|

### 2022-11-14 revision_letter.Rmd
Closes #17

This is our response: For example, instructors can include accessibility as one of their evaluation criteria for course assignments or make it as a chance to obtain bonus credits for the students' visualization work.

> This is a section quoted from the revised manuscript to illustrate the change.

>>>>

We have clarified this point with the following sentence, in addition to the original sentence in the `Closing Remarks` section.

> We believe that an accessible future in data science requires educators to teach accessibility as part of the curriculum deliberately. 
This includes both teaching the topic as well as assessing it so that students are held accountable for their accessibility practices.

Please note that we had also the following section in the original manuscript which we have also kept in the revised version.

> Ample opportunities in learning accessibility should also include assessments. 
For instance, instructors should modify assessment instructions and rubrics to include accessibility. 
This will prevent students from just hearing about accessibility in the lecture and then forgetting about it. 
Ideally, the assessments should not treat accessibility as a learning objective at a single point in the academic term. 
For instance, if accessibility is covered in Week 3 of the term, students can (and should) still be expected to write alternate texts for visualizations until the end of the semester.
